Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-30 paper/lostanlenRelevanceScattering.tex
rewrite one paragraph in dataset section

The experiments in this paper are carried out on the DCASE 2013 dataset~\cite{7100934}.
Although the dataset was constructed for the task of acoustic scene classification, where the goal is to correctly assign the class of a given recording, we can use the same recordings and class labels for the task of acoustic scene similarity retrieval.
The dataset consists of two parts, a public and a private subset, each made up of $100$ acoustic scene recordings sampled at $44100\,\mathrm{Hz}$ and $30$ seconds in duration. The dataset is evenly divided into $10$ acoustic scene classes: \emph{bus}, \emph{busy street}, \emph{office}, \emph{open air market}, \emph{park}, \emph{quiet street}, \emph{restaurant}, \emph{supermarket}, \emph{tube}, and \emph{tube station}.
The recordings were made by three different recordists at a wide variety of locations in the Greater London area over a period of several months.
No systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a result, the dataset enjoys significant intra-class diversity while remaining of manageable size, making it suitable for evaluation of algorithmic design choices~\cite{lagrange:hal-01082501}.

>>>>

The experiments in this paper are carried out on the DCASE 2013 dataset~\cite{7100934}.
Although the dataset was constructed for the task of acoustic scene classification, where the goal is to correctly assign the class of a given recording, we can use the same recordings and class labels for the task of acoustic scene similarity retrieval.
The dataset consists of two parts, a public and a private subset, each made up of $100$ acoustic scene recordings sampled at $44100\,\mathrm{Hz}$ and $30$ seconds in duration. The dataset is evenly divided into $10$ acoustic scene classes: \emph{bus}, \emph{busy street}, \emph{office}, \emph{open air market}, \emph{park}, \emph{quiet street}, \emph{restaurant}, \emph{supermarket}, \emph{tube}, and \emph{tube station}.
The recordings were made by three different recordists at a wide variety of locations in the Greater London area over a period of several months.
In order to avoid any correlation between recording conditions and label distribution, all recordings were carried out under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a result, the dataset enjoys significant intra-class diversity while remaining of manageable size, making it suitable for evaluation of algorithmic design choices~\cite{lagrange:hal-01082501}.
